\vspace{-15mm}\fontsize{16pt}{10pt}\selectfont\textbf{Facial Expression Recognition with\\ Convolutional Neural Networks}

### 2018-03-03 doc/paper.tex
bibliography

\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

\bibitem[http://fluidos.eia.edu.co/]{Figueredo:2009dg}

\newblock {\em Fluidos, Carlos Toro s.}

\bibitem[http://www.windows2universe.org/]{Figueredo:2009dg}

\newblock {\em Becca Hatheway}

\bibitem[http://meteorologia.pucp.edu.pe/]{Figueredo:2009dg}

\newblock {\em Hernan Castillo, Pedro Ríos}

\bibitem[http://www.ammonit.com/Manuales]{Figueredo:2009dg}

\newblock {\em Ammonit Measurement GmbH}

>>>>

\begin{thebibliography}{9}

	% OpenCV Haarcascade Classifier
	\bibitem{violajones}
  	P. A. Viola and M. J. Jones. Robust real-time face detection.
	International Journal of Computer Vision
	57(2):137–154, 2004.

	% the ICML 2013 workshop’s facial expression recognition challenge
	\bibitem{replearning}
	I. J. Goodfellow et al.
	Challenges in representation learning: A report on three machine
	learning contests.
	Neural Networks
	, 64:59 – 63, 2015.
	Special Issue on ‘Deep Learning of Representations’
